\documentclass{article}
\usepackage{hyperref}
\title{The Sudoku Project}
\author{Ishika De and Yashvi Donga}
\date{}

\begin{document}
    \maketitle
    \section{Objective}
    The goal of this project is to investigate a variety of algorithms
    (backtracking, brute force, stochastic search and Crook’s algorithm) that
    are capable of solving sudoku puzzles, of ranging difficulties, in order to
    learn more about sudoku solving techniques.\\
    We also wanted to use the OpenCV library to read a sudoku from an
    image and solve it.
    \section{Toolchain}
    \begin{itemize}
        \item Languages: Python, C++, Java.
        \item Libraries used in Python: Numpy, OpenCV and Keras.
    \end{itemize}
    \section{Challenges}
    \section{Learnings}
     We learnt to:
     \begin{itemize}
		 \item Collaborate using GitLab.
		 \item Write the same algorithm in different languages.
		 \item Generate data in one language and use the data in another language.
		 \item Explain our code, thought processess and ideas to each other.
		 \item Apply the concept of cost function and thermodynamics in simulated annealing.
		 \item Generate 100 sudokus of 3 different difficulty levels.
		 \item Process an image to extract digits of a sudoku.
		 \item Implement neural networks to predict digits of a sudoku from an image.
	 \end{itemize}
    \section{Results and Conclusion}
     
    \section{Code Repository} 
    Our code repository link: \href{https://gitlab.com/yashvidonga29/sudoku-project-we}{\emph{https://gitlab.com/yashvidonga29/sudoku-project-we}}
    \section{References}   
    \begin{itemize}
        \item \nolinkurl{http://people.uncw.edu/tagliarinig/Courses/380/F2015%20papers%20and%20presentations/F2015%20papers%20and%20presentations/Sudoku/Sudoku.pdf}
        \item \nolinkurl{https://towardsdatascience.com/solving-sudoku-with-ai-d6008993c7de}
        \item \nolinkurl{http://zhangroup.aporc.org/images/files/Paper_3485.pdf}
        \item \nolinkurl{https://www.sudokuwiki.org/Brute_Force_vs_Logical_Strategies}
        \item \nolinkurl{https://stacks.stanford.edu/file/druid:my512gb2187/Agarwal_Kamat_Kurian_Smart_Sudoku_Solver.pdf}
        \item \nolinkurl{https://blogs.mathworks.com/deep-learning/2018/11/15/sudoku-solver-image-processing-and-deep-learning/}
        \item \nolinkurl{https://www.researchgate.net/publication/264572573_Sudoku_Puzzle_Complexity}
        \item \nolinkurl{https://www.youtube.com/watch?v=FyyVbuLZav8}
        \item \nolinkurl{https://www.adrian.idv.hk/2019-01-30-simanneal/}
        \item \nolinkurl{https://link.springer.com/article/10.1007/s10732-007-9012-8}
        \item \nolinkurl{https://docs.opencv.org/4.5.2/d0/de3/tutorial_py_intro.html}
        \item \nolinkurl{https://www.youtube.com/watch?v=aircAruvnKk}
    \end{itemize}
\end{document}